
%%%%%%%%%%
%CNC ROOM
%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%: Large CNC Cutter
\machinePage{Large CNC Cutter}{}{
}{
\action{51}{Ear protection strongly recommended}{Note also that this machine should not be used after 19:00}
\action{52}{Eye protection recommended}{Especially when using very small cutters.}
\action{64}{Wear a mask when needed}{Especially when cutting materials such as MDF}
\warn{124}{Machine can suddenly start}{%
	Machine can suddenly start moving; and can move under its own command (even when the PC is off -- rely on the emergency stop buttons.).
	
	It will also start moving without warning -- for example when the PC\&software are (re)started.}
\warn{130}{Crushing}{Risk of crushing -- the machine does not have any sensors that detect obstacles
This includes things such as your hands (do not lean on the blue rail) or tools you've left on the workspace.
}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%: Abene
\machinePage{Abene Mill}{Induction}{
}{
\prohib{100}{Do not wear gloves}{Especially strong leather ones. They get caught easily and then `help' ripping body parts off.}
\action{52}{Eye protection recommended}{Swarf will fly. Cutters can come loose. Broken cutters can fly very far and are razor sharp.}
\action{58}{Wear protective clothing}{Wear tight fitting clothing, keep long hair tied up, no jewellery or anything else that can be caught by the machine.}
\warn{125}{Crushing}{Risk of crushing -- the machine does not have any sensors that detect obstacles.

Note that it can also run very slow; barely noticeable.}
\warn{117}{Slippery surface}{Floor will get very slippery; especially when using coolant.}
\warn{128}{Sharp rotating elements}{This machine is essentially a cutter without any guard whatsoever.}
}{
Only switch XYZ feeds when the machine is not running. Use the hand-wheel to get the gear fully locked in prior to starting the feed. Be sure to tighten all 4 nuts post rotating the head or all 4 nuts when moving the head laterally.

Try to avoid getting coolant or similar on the slide-ways -- especially the Y slipway between machine and table. Use a shield or adjust the flow. Machine needs to be cleaned post use.  When using coolant -- also empty the recess on the left of the table and clean out the t-Slots until dry.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%: Grote Laser
\machinePage{Large CNC Laser cutter}{Logbook}{
Be sure to check that cooling, air assist and fume extraction fan are all on.
}{
\warn{84}{Do not extinguish with water}{It has a high voltage (kV) power supply. Use the $CO_2$ extinguisher (on the pilar to your left). }
\warn{110}{Laser beam}{Keep the lid closed at all times. If you bypass the safety interlocks -- you are an idiot.}
}{
Do not forget to switch on (and off post use) the compressor and fume extraction fan (in the corner near the electric distribution board.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%: Kleine Laser
\machinePage{Small CNC Laser cutter}{Extraction}{
Be sure to check that water cooling pump, air pump (behind the machine) and fume extraction fan are all on.
}{
\warn{84}{Do not extinguish with water}{It has a high voltage (kV) power supply. Use the $CO_2$ extinguisher (on the pilar to your left).}
\warn{110}{Laser beam}{Keep the lid closed at all times. If you bypass the safety interlocks -- you are an idiot.}
}{
Do not forget to switch the fume extraction fan (in the corner near the electric distribution board) post use.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%:   Ultimakers
\machinePage{Ultimaker 2 \& 2$^{+\mathsf{Extended}}$}{}{
Do not walk away from the machine until the first 10 layers or so have been deposited. 

OK to leave unattended after first 10 minutes when used with normal settings/materials.
}{
\warn{124}{Automatic start-up}{Machine may suddenly start moving. Also during power up.}
\warn{123}{Hot surfaces}{The bed and the head will become (very) hot.}
}{
Keep the filament in a sealed container. Exposure to air (humidity) makes it brittle.
}


%%%%%
% Main Room
%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%: CNC Vinyl snijder
\machinePage{CNC Vinyl cutter}{}{
}{
\warn{128}{Sharp rotating elements}{}
\warn{124}{Machine can suddenly start}{Also during power-up.}
}{
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%: Ultrasonic Cleaner
\machinePage{Ultrasonic cleaner}{NoMandatory}{
Contains cleaning solvent (10\% dilution) -- keep off skin and out of your eyes.

When using aggressive solvents - use small jars within the normal cleaning fluid. To avoid damaging or corroding the tank/metal.
}{
\action{57}{Wear protective gloves}{}
\action{52}{Eye protection recommended}{Especially when using aggressive solvents}
\action{58}{Protective clothing recommended}{E.g. to protect your bare arms, etc.}
\warn{49}{Irritant, Corrosive}{Water contains cleaning solvent}
\warn{49}{Hot}{Water will be hot}
}{
Noise wise -- be considerate to our neighbours -- especially in the evenings.


Do not run unattended.  Stay at the space when it is in use or when it is still hot.
}


%%%%%
%Electronics Area
%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%:  Reflow oven
\machinePage{PCB Reflow Oven}{}{
}{
}{
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%:  Hot plate
\machinePage{T-Shirt hotplate}{}{
}{
\warn{123}{Hot surfaces}{The hotplate will become hot (obviously).}
}{
}











%%%%%
% Not in Bristol Hackspace (yet)
%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%:  Welding kit and gas
%\machinePage{Welding equipment}{Log}{
%Gas cylinders must be kept mounted in their stand with a \textbf{safety strap} at all times.

%There should never be more than a total125L of `water equivalent' volume, aggregated across all bottles (full or empty) at the space.
%}{
%\action{67}{Wear a welding mask}{}
%\action{57}{Wear protective gloves}{}
%\warn{128}{Pressurised Cylinders}{}
%\action{74}{Use protective apron}{}
%}{
%Do not forget to close the valves on the gas bottles post use.

%If you have empty bottles; be sure to get them refilled or remove them from the space. 

%There should \textbf{never be more than a 125 litres} of `water equivalent' volume present at the space (aggregated across all cylinders, \textbf{empty or full}, pressured or unpressured).

%This is because the space does \textbf{not have the required permits} for crossing the \textbf{125L limit}.
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%:   Pottery oven
%\machinePage{Pottery Oven}{Mandatory}{
%This oven is for pottery, ceramics, annealing and similar use. Up to 1200\degree C.

%Please write down the electricity use (kWh counter) and pay \euro{0.25} to the foundation (NL30 TRIO 0197 6945 19).
%}{
%\prohib{75}{No mid-bake opening}{This oven is not designed to be opened while hot. Or to have contents removed (or added) while hot.}
%\prohib{75}{No fumes}{This oven has no exhaust. So no metal melting or similar.}
%\warn{118}{Bare electric wires inside}{Do not open the oven while powered on. The heating spirals are not isolated.}
%}{
%Stay with the machine while it is powered.
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%: Blacksmithing Oven
%\machinePage{Blacksmithing Oven}{Mandatory, Two}{

%When using - make sure the that you have ready access to the main shut-off valve (i.e. so you do not have to reach over something hot) and that the tubing is well out of harms way.

%Keep track of your gas use \& report this.
%}{
%\warn{49}{Hot}{Oven will be hot}
%\action{57}{Wear protective gloves}{}
%\action{52}{Eye protection recommended}{}
%\action{58}{Protective clothing recommended}{}
%\action{49}{No abrasive work or grinding allowed while the oven is in operation.}{}
%}{
%Noise wise -- be considerate to our neighbours -- especially in the evenings.

%Do not run unattended.  Stay at the space when it is in use or when it is still hot. If it is still hot when you leave; make sure this is clearly signposted.
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%: Jung Surface Grinder
%\machinePage{Jung Surface Grinder}{Induction}{
%Be very gentle with the Z-axis; do not plunge or ram it into the surface.

%If you notice any imbalance - stop immediately. Disk or machine can quickly destroy themselves.
%}{
%\prohib{75}{Carbide Aluminium Forbidden}{It is forbidden to grind Aluminium. Just don't. No carbide either}
%\action{52}{Eye protection mandatory}{Sparks will fly, the grinding disk can shatter}
%\action{58}{Wear protective clothing}{Wear tight fitting clothing, keep long hair tied up, no jewellery or anything else that can be caught by the machine.}
%% \prohib{100}{Do not wear gloves}{Especially strong leather ones. They get caught easily and then `help' ripping body parts off.}
%\warn{125}{Crushing}{Risk of crushing -- the machine does not have any sensors that detect obstacles.}
%\warn{124}{Grinding wheel runs `invisibly}{%
%The grinding wheel will run very smooth, barely visible - and will continue to be dangerous for a minute or so after shutoff
%}
%\warn{117}{Slippery surface}{Floor will get very slippery; especially when using coolant.}
%\action{64}{Wear a mask when needed}{And be very careful with truly nasty material. Grinding carbide is not allowed.}
%\warn{108}{Explosion risk}{Aluminium Forbidden: Explosion risk in general; and especially in combination with rust/water based coolant}
%}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%: 12 ton press
%\machinePage{Hydraulic Press}{}{
%}{
%\action{52}{Eye protection needed}{}}{
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Zandstraalcabine
%\machinePage{Sanding Cabinet}{}{
%Do not spray at your hands/fingers. The gloves \textbf{will} ultimately give way and they are not cheap.
%}{
%}{
%Do switch off the compressor after use.
%}
