%%%%%
%Metal Room
%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%: Metal Lathe
\machinePage{Metal Lathe}{Induction}{
Be careful when using the auto-feed; especially with cutters near the revolving head.
}{
\prohib{100}{Do not wear gloves}{Especially strong leather ones. They get caught easily and then `help' ripping body parts off.}
\action{52}{Eye protection recommended}{Swarf will fly. Cutters can come loose. Broken cutters can fly very far and are razor sharp.}
\action{58}{Wear protective clothing}{Wear tight fitting clothing, keep long hair tied up, no jewellery or anything else that can be caught by the machine.}
\warn{125}{Crushing}{Risk of crushing -- the machine does not have any sensors that detect obstacles.

Note that it can also run very slow; barely noticeable.}
\warn{117}{Slippery surface}{Floor may get slippery when using coolant.}
% \warn{128}{Sharp rotating elements}{This machine is essentially a cutter without any guard whatsoever.}
}{
Clean after use -- especially when you have used coolant or have used metals that can rust easily or cause a galvanic reaction.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%: Slijpsteen
\machinePage{Large Grinder}{}{}{
\action{58}{Wear protective clothing}{Wear tight fitting clothing, keep long hair tied up, no jewellery or anything else that can be caught by the machine.}
\action{52}{Eye protection needed}{}
\action{51}{Ear protection recommended}{}
}{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%: Metaal zaag
\machinePage{Metal bandsaw}{}{
Use plenty of cutting oil, \textsc{wd40} or similar. 

Do not leave unattended (not in the least as you may want to keep lubricating it to get a nice cut).
}{
\action{58}{Wear protective clothing}{Wear tight fitting clothing, keep long hair tied up, no jewellery or anything else that can be caught by the machine.}
\warn{128}{Sharp rotating elements}{}
\action{52}{Eye protection recommended}{}
}{
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%: Metal Bandsaw
\machinePage{Metal bandsaw}{}{
Suitable for metal; hard wood and some types of plastics. 
}{
\action{58}{Wear protective clothing}{Wear tight fitting clothing, keep long hair tied up, no jewellery or anything else that can be caught by the machine.}
\action{52}{Eye protection recommended}{}
\action{51}{Ear protection recommended}{Note also that this machine should not be used after 19:00 if it is that noisy}
\warn{128}{Sharp rotating elements}{Bypassing or using your fingers to hold the guard open is downright stupid.}
}{
Use of cutting oil recommended !
% No special comments/instructions.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%: Hembrug Metal Drill Press
\machinePage{Hembrug Drill press}{Mandatory}{
Make sure you clamp your workpiece well - to avoid spinning.

Let the drill do its work - do not apply much pressure (drill gets dull or will snaps).

Use the correct drill speed (higher for aluminium, low for steel, very low for stainless steel (\textsc{rvs}). Use the table on the wall.

Use drilling oil when needed (when in doubt - always use the green oil).
}{
\action{52}{Eye protection recommended}{Sharp bits will fly, drills snap.}
\action{58}{Wear protective clothing}{Wear tight fitting clothing, keep long hair tied up, no jewellery or anything else that can be caught by the machine.}
\prohib{100}{Wearing gloves is forbidden}{Especially strong leather ones. They get caught easily and then `help' ripping body parts off. 
}}
{
\textbf{Beware that this is a powerful, 3-phase (Krachtstroom), machine.}

So unlike the other pillar-drill - it won't stop of something jams.

Beware that the machine can start to spin if you press the green button while the rotary knob is set to 1 or 2. 

Only use the emergency button on the front for emergency stops. For routine on-off use the rotary knob. De-energise the machine with the red button when you are done.

Noise wise -- be considerate to our neighbours -- especially in the evenings.
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%: Drill & Mill
\machinePage{Drill \& Mill}{NoMandatory}{
\textbf{Drilling}: Use with common sense, do not drill in the metal of the XY table! Use the wooden overlay to protect it. 

\textbf{Milling}: Getting instructions \textbf{prior} to use is mandatory. After milling: put the machine back in order for drilling, so others can use it

\textbf{When changing the drillbit for milling: use a nylon hamerhead, do NOT use a metal hamer.  }
}{
\prohib{100}{Do not wear gloves}{Especially strong leather ones. They get caught easily and then `help' ripping body parts off. 

Very thin (latex) gloves that easily tear are ok.}
\action{52}{Eye protection recommended}{Especially when milling. Swarf will fly. Cutters can come loose. Broken cutters can fly very far and are razor sharp.}
\action{58}{Wear protective clothing}{Wear tight fitting clothing, keep long hair tied up, no jewellery or anything else that can be caught by the machine.}
\warn{128}{Sharp rotating elements}{This machine is essentially a cutter without any guard whatsoever.}
\warn{117}{Slippery surface}{Floor will get very slippery; especially when using coolant.}
}{
To adjust the height: 1) loosen the lower nut at the right back side of the machine (marked: 'deze moer' ). Then 2) use the big handle on the left side to crank up/lower the whole top part of the drill. \\
\textbf{And 3) fasten the nut again before drilling!}

For speed adjustment open the top and re-arrange the belts as shown on the diagram on the machine for the right speed. You can run these off/on the wheels by starting and ending with the larger of the two.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%: Metal Sander
\machinePage{Metal Sander}{}{
This machine is for metal sanding - both ferrous and non-ferrous metals are allowed (until further notice).

\textbf{Connect a shopvac/vacuum cleaner to keep the dust under control.}

}{
\action{58}{Wear protective clothing}{Wear tight fitting clothing, keep long hair tied up, no jewellery or anything else that can be caught by the machine.}
\action{51}{Ear protection recommended}{Note also that this machine should not be used after 19:00 -- it is that noisy!}
\action{52}{Eye protection recommended}{}
\action{64}{Wear a mask when needed}{And keep the dust under control by connecting the vacuum cleaner or a shop vac. The grit is both unhealthy \& damaging to other equipment.}
\warn{128}{High speed abrasive surfaces}{So keep your fingers away.  

It takes metal away awfully fast.}{}
}
{Consult the WIKI (or ask) when you need to change the sanding belt. Report this on the mailing list.

Try to leave the machine in at least as clean a state as you found it. Likewise, if you `gum up' the sanding belt (easy with for example soft aluminium) -- do feel encouraged to replace it or at least warn the next user via the mailing list.
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%:   Drill press
\machinePage{Oscillating Band/Bobbin Sander}{NoMandatory}{
This machine is for WOOD only.

Make sure that the bobbin/band is fixed in position and cannot slip. 

Let the sander do its work - do not apply much pressure (things will burn, you'll ruin the mechanics).
}{
\action{49}{Dust extraction mandatory}{Use the dust extractor. Always.}
\action{64}{Wear a mask when needed}{Depending on the wood being sanded.}
\action{52}{Eye protection recommended}{}
\action{58}{Wear protective clothing}{Wear tight fitting clothing, keep long hair tied up, no jewellery or anything else that can be caught by the machine.}
}{
Noise wise -- be considerate to our neighbours -- especially in the evenings.
}

